### 2013-10-18 chi2014/conclusions.tex
down to 11 pages...

Our results show that ideas are more likely to be followed by one from the same category, and that changing categories takes time. Combining these models with others (such as natural language measures for text similarity), one could imagine constructing a posterior belief model to infer whether a participant is currently riffing or not. If we can infer riffing and the general categories in which workers are riffing, one could imagine techniques to guide the crowd to explore different areas of the design space. For example, the system could encourage workers to generate ideas within new or rare categories.

@@

\begin{itemize}
\item The rate of idea and category generation decays non-linearly over time. 
\item Common ideas are more likely to be proposed early in a run. 
\item Conversely, ideas beyond the first 20 are rarer and more original, as measured by o-scores. This relationship also holds for idea categories.
\item Ideas are more likely to be followed by another idea from the same category than would be expected by random chance.
\item The time it takes to generate an idea when changing categories is longer than the time taken when generating ideas within a category.
\item There are repeatedly observable strategies employed by workers brainstorming in microtask marketplaces
\end{itemize}

>>>>

Our results show that ideas are more likely to be followed by one from the same category, and that changing categories takes time. One could imagine constructing a posterior belief model to infer whether a participant is currently riffing or not, guide the crowd to explore ideas within new or rare categories.

@@

\begin{itemize}
\item The rate of idea and category generation decays non-linearly over time. 
\item Common ideas are more likely to be proposed early in a run. 
\item Conversely, ideas beyond the first 20 are rarer and more original, as measured by o-scores. %This relationship also holds for idea categories.
\item Ideas are more likely to be followed by another idea from the same category than would be expected by random chance.
\item The time it takes to generate an idea when changing categories is longer than the time taken when generating ideas within a category.
\item There are repeatedly observable strategies employed by workers brainstorming in microtask marketplaces
\end{itemize}

### 2013-10-18 chi2014/goals.tex
10 page revision first attempt
down to 11 pages...

In modeling these quantities, we wish to explore the following hypotheses:

@@

\textbf{Hypothesis 3:} O-scores generated in the second half of a brainstorming session will be higher than ideas generated in the first half. This hypothesis provides a complementary perspective to the former.

@@

\textbf{Hypothesis 4:} An idea from one semantic category of ideas should more often be followed by an idea from the same category than expected by random chance.

\textbf{Hypothesis 5:} The time it takes to generate an idea should be longer when changing semantic categories than when generating ideas within a category.

>>>>

In modeling these quantities, we explore the following hypotheses:

@@

%\textbf{Hypothesis 3:} O-scores generated in the second half of a brainstorming session will be higher than ideas generated in the first half. This hypothesis provides a complementary perspective to the former.

@@

\textbf{Hypothesis 3:} An idea from one semantic category of ideas should more often be followed by an idea from the same category than expected by random chance.

\textbf{Hypothesis 4:} The time it takes to generate an idea should be longer when changing semantic categories than when generating ideas within a category.

### 2013-10-18 chi2014/introduction.tex
down to 11 pages...

A particularly compelling use of microtask marketplaces is to tap into the collective creativity of crowds. This enables one to quickly sample a wide range of ideas from a diverse population for tasks such as brainstorming or design. Aaron Koblin's art piece ``The Sheep Market'' \cite{koblin_2009} was an early demonstration of this application. In this project, he asked 10,000 individuals to draw a ``sheep facing left,'' yielding a wide range of unique results. More recently, there has been interest in systems that support crowd-based design. For example, Yu and Nickerson developed a system that combines genetic algorithms with design input from crowd workers to explore a design space \cite{yu_cooks_2011}.

@@

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. 
\item We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 15).
\item we identify and describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

>>>>

A particularly compelling use of microtask marketplaces is to tap into the collective creativity of crowds. This enables one to quickly sample a wide range of ideas from a diverse population for tasks such as brainstorming or design. Aaron Koblin's art piece ``The Sheep Market'' \cite{koblin_2009} was an early demonstration of this application. In this project, he asked 10,000 individuals to draw a ``sheep facing left,'' yielding a wide range of unique results.

@@

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item we identify and describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

### 2013-10-18 chi2014/method.tex
down to 11 pages...

\subsection{Brainstorming Question: Uses for an Old MP3 Player}
In conducting this research, we tested several brainstorming questions, including classic brainstorming questions (e.g., ``provide alternative uses for a mop''); a request to brainstorm factors that influence weight gain and weight loss; and more goal-oriented questions, such as one requesting people to brainstorm ways to raise funds for a charity. Ultimately, we found the goal-oriented brainstorming questions to be the most compelling since they reflect what we believe would be real-world uses of brainstorming on Mechanical Turk.

@@

In addition to the visible text input fields, HITs were instrumented to collect timing data. Specifically, we recorded the time of the first activation and last de-activation of each form element, the time the HIT was accepted, and the time it was submitted.

@@

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the possibility that their responses and idea generation processes evolved over time. Accordingly, we retain only the first HIT submitted by each worker.

@@

\begin{table}[h!]
\begin{tabular}{r | l l l l l l l }
    & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline
    participants & 57 & 39 & 21 & 9 & 10 & 10 & 146 \\
    solutions & 283 & 372 & 413 & 450 & 635 & 855 & 3007
\end{tabular}
\caption{Data after removing unlimited condition and repeats}
\label{tab:data_collected}
\end{table}

@@

\subsection{Hierarchical Clustering}
One of the primary goals of this research is to model the rate at which novel ideas and categories of ideas arrive. A significant challenge to creating these models is efficiently identifying what ideas and categories of ideas are similar to one another. To address this problem, we organized the data into sets of hierarchical clusters, where parent nodes are more generalized versions of child nodes. With this relationship, we are then able to calculate quantities such as the rate of novel ideas or novel idea categories, as a function of responses received.

@@

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, though multiple instances can be associated with the same idea (i.e., when multiple workers come up with the same idea). Multiple instances of the same idea do not need to be identically phrased to refer to the same idea. For example, in Figure~\ref{fig:example_instances}, we consider ``Storage Container'' and ``Small Storage Box'' as two instances of the same \emph{idea}. However, we do not consider ``Coin Storage'' to be the same idea, since it provides a more specific use case than the previous two.

Despite the differences in specificity between ``Coin Storage'' and the more generic containers, it is useful to encode the fact that these ideas are related. We use hierarchical clusters to encode these relationships. We call a hierarchical cluster of ideas a \emph{category tree}.

>>>>

\subsection{Brainstorming Question: Uses for an Old MP3 Player}
In conducting this research, we tested several brainstorming questions, including classic brainstorming questions from prior work (e.g., ``provide alternative uses for a mop''); a request to brainstorm factors that influence weight gain and weight loss; and more goal-oriented questions, such as one requesting people to brainstorm ways to raise funds for a charity. Ultimately, we found the goal-oriented brainstorming questions to be the most compelling since they reflect what we believe would be real-world uses of brainstorming on Mechanical Turk.

@@

In addition to the visible text input fields, HITs were instrumented to collect the time of the first activation and last de-activation of each form element.

@@

If a worker completed multiple HITs, there is the possibility that their responses and idea generation processes evolved over time. Accordingly, we retain only the first HIT submitted by each worker.

@@

%\begin{table}[h!]
%\begin{tabular}{r | l l l l l l l }
%    & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline
%    participants & 57 & 39 & 21 & 9 & 10 & 10 & 146 \\
%    solutions & 283 & 372 & 413 & 450 & 635 & 855 & 3007
%\end{tabular}
%\caption{Data after removing unlimited condition and repeats}
%\label{tab:data_collected}
%\end{table}

@@

\subsection{Hierarchical Clustering}
A significant challenge to creating model of brainstorming is efficiently identifying what ideas and categories of ideas are similar to one another. To address this problem, we organized the data into sets of hierarchical clusters, where parent nodes are more generalized versions of child nodes. %With this relationship, we are then able to calculate quantities such as the rate of novel ideas or novel idea categories, as a function of responses received.

@@

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, though multiple instances can be associated with the same idea. Multiple instances of the same idea do not need to be identically phrased to refer to the same idea. For example, in Figure~\ref{fig:example_instances}, we consider ``Storage Container'' and ``Small Storage Box'' as two instances of the same \emph{idea}. However, we do not consider ``Coin Storage'' to be the same idea, since it provides a more specific use case than the previous two.

Despite the differences in specificity between ``Coin Storage'' and the more generic containers, it is useful to encode their relationship. We use hierarchical clusters to encode these relationships. We call a hierarchical cluster of ideas a \emph{category tree}.

### 2013-10-18 chi2014/qualitative.tex
down to 11 pages...

We selected 30 brainstorming runs (5 randomly from each condition). The primary author applied an open coding strategy, identifying classes of ideas within runs that hold common characteristics. For each class that was observed across multiple participants, we infer the existence of a \emph{strategy}: a plan or rule that aids in generating ideas. We describe the observed strategies in detail below.
We describe the distribution of these strategies across runs and comment on variability between participants.

@@

A \emph{strategy} is a plan or rule, that is used by a participant to generate brainstorming responses.
We identified 3 \emph{orthogonal} strategy categories - each category of strategies can be employed by a participant with or without any of the other categories.
The first, \emph{problem scoping}, is a process in which a participant chooses a limited implication or component of the problem and provides multiple specific solutions.
The second category expands on the \emph{riffing} phenomenon introduced earlier, identifying 4 different types of riffing.
%Finally, the \emph{humour} strategy emphasizes generating ideas that are amusing rather than practical.
Finally, the \emph{partial solution} strategy entails creating an idea that requires further idea generation to solve the problem.

@@

Under the problem scoping strategy, the original problem is transformed to a new problem of reduced scope.
Many transformations of the MP3 problem are possible, for example: brainstorm uses for \emph{an audio output device}; brainstorm uses for a small box-shaped object; brainstorm uses for \emph{a hard drive}; and so on. The participant chooses a problem transformation and generates solutions, each of which is also a solution to the original problem. For example (PXXX):

\begin{itemize}
    \item have them as a resource on public transportation -- people must supply their own headphones
    \item use them in museums to give information on various installations
    \item have cities install them in tourist areas, so people can listen about where they are
\end{itemize}

@@

\emph{Outward scoping} transformations reduce complexity by stripping all meaningful details. For example (PXXX):

@@

Another type of riffing is \emph{repeat riffing}. Under this strategy, a participant produces multiple responses with only slight differences between them, such that the group of ideas could be easily summarized as one idea without significant loss of information. For example (PXXX):

@@

\emph{Hold riffing} is a strategy in which participants hold at least one element of a previous response constant when generating a new response, such that a new idea is formed. For example (PXXX):

@@

\emph{Continuation riffing} is the strategy of creating another idea that relies on the implications or consequences of a previous idea. The new idea cannot be understood without the context of the previous. For example (PXXX):

@@

The strategies above describe techniques for taking one idea and transforming it into another. In this section, we describe patterns of \emph{where} participants implemented these strategies.

@@

Finally, some participants \emph{pair} their riffs. Paired riffing is a special case on linear riffing in which only a single riffed idea is produced, and no further riffs are produced on that source for the remainder of the run. For example, paired repeat riffing from PXXX:

@@

\begin{itemize}
    \item use old parts to make a new device
    \item old parts can use to make something
    \item create a new device
\end{itemize}

In these responses, there is a clear recommendation that we recycle components of the MP3 player to produce new electronics, but it is unclear what we would make or how we would use the parts.

There are four sub-strategies of partial solutions: problem scoping without solution, goal without plan, plan without goal, and passing the problem. 
In some responses, an end goal has been established, but any implementation of the goal requires further idea generation. We call this strategy \emph{goal without plan}. The above responses are examples of the goal without plan strategy.
The goal of creating a new electronic device is given, but it is not clear what will be created or how the materials will be re-used.

@@

Above, we described the problem scoping strategy. Some participants performed \emph{problem scoping without solution}, in which problem scoping is the only component of the response.
For example, one of PXXX's responses to the MP3 player problem was to "Remove glass screen to make something". In this case, the participant has provided a scoping of the problem (focus on the glass component) but has not actually provided a solution to the scoped problem.

@@

@@

These solve the original problem, but simultaneously re-open the problem under slightly changed conditions. In this case, a third party must determine what to do with broken MP3 players.

@@

In this section, we DESCRIBE how strategies were employed by participants. The primary author again coded 30 randomly selected runs (5 from each condition, 1150 instances total) for the strategies identified above. Note that examples of riffing identified in this section are distinct from the category tree identification of riffing described in the method section above. The prevalence of each strategy as a function of total number of instances is given in Table TAB, and a comparative plot in Figure FIG.

\begin{table}
    \begin{tabular}{r | l l}
        \textbf{strategy} & \textbf{\# instances} & \textbf{\% of instances} \\
        inward scoping & 267 & 23.2 \\
        outward scoping & 828 & 72 \\
        no scoping & 55 & 4.8 \\
        \hline \hline
        hold riffing & 278 & 24.2 \\
        continuation riffing & 3 & 0.3 \\
        repeat riffing & 119 & 10.3 \\
        generalization riffing & 48 & 4.2 \\
        \hline
        any riffing & 448 & 39.0 \\
        pair & 108 & 9.4 \\
        reach back & 129 & 11.2 \\
        \hline \hline
        scoping without solution & 3 & 0.3 \\
        passing the problem & 69 & 6 \\
        plan without goal & 58 & 5.0 \\
        goal without plan & 58 & 5.0 \\ 
        \hline
        any partial solution & 188 & 16.3 \\
    \end{tabular}
\end{table}

@@

Outward scoping is by far the most commons strategy, occurring in 72\% of instances. Riffing is also very common, with 40\% of instances employing some form of riffing. Riffs are most often consecutive (linear riffing), and hold riffing is the most common type.

@@

The distributions of strategy occurence across position in run tend towards uniform when there are more than a few examples. The notable exception to this is problem scoping. There are fewer occurences of the inward scoping strategy later in brainstorming runs.

The number of reach-backs increase with position. This may simply be because there are more ideas to draw from for inspiration later in a run.

@@

\begin{itemize}
\item With displays - could be attached to a small solar panel (like the USB chargers w/multi attachments, including solar and car, etc.) and all the power could be sent to the screen as a small, portable light, then sent to countries lacking power in rural areas.
\item They could be loaded with coordinates or other info and sealed in containers, then used in ocean current studies - once the container was collected they could be plugged in and read, and the data could be sent to whomever.
\item They could be plugged in at a base camp at the bottom of Everest, and then potential climbers could record their name, loved ones' address, and any last words before attempting the climb. 
\end{itemize}

This individual's responses were responsible for clearly raising the observed uniqueness of ideas in the 75 condition when plotted against the other conditions.
In contrast, other individuals filled their quotas with excessive repeat riffing chains.

>>>>

We selected 30 brainstorming runs (5 randomly from each condition). The primary author applied an open coding strategy, identifying \emph{strategies}: plans or rules that aid in generating ideas. We describe the observed strategies in detail below.
We describe the distribution of these strategies across runs and comment on variability between participants.

@@

A \emph{strategy} is a plan or rule, that is used by a participant to generate brainstorming responses. We infer the existence of strategies through similar classes of ideas observed between participants.
We identified 3 strategy categories, each of which can be employed with or without any of the other categories.
The first, \emph{problem scoping}, is a process in which a participant chooses a limited implication or component of the problem and provides multiple solutions.
The second category expands on the \emph{riffing} phenomenon introduced earlier.
%Finally, the \emph{humour} strategy emphasizes generating ideas that are amusing rather than practical.
Finally, the \emph{partial solution} strategy entails creating an idea that requires further idea generation to solve the problem.

@@

Under the problem scoping strategy, the original problem is transformed to a new problem of reduced scope.
Many transformations of the MP3 problem are possible, for example: brainstorm uses for \emph{an audio output device}; brainstorm uses for \emph{a hard drive}; and so on. The participant chooses a problem transformation and generates solutions, each of which is also a solution to the original problem. For example (PXXX):

\begin{itemize}
    \item have them as a resource on public transportation -- people must supply their own headphones
    \item use them in museums to give information on various installations
    %\item have cities install them in tourist areas, so people can listen about where they are
\end{itemize}

@@

\emph{Outward scoping} transformations reduce complexity by stripping meaningful details. For example (PXXX):

@@

Another type of riffing is \emph{repeat riffing}. Under this strategy, a participant produces multiple responses, such that the group of ideas could be easily summarized as one idea without significant loss of information. For example (PXXX):

@@

\emph{Hold riffing} is a strategy in which participants hold at least one element of a previous response constant when generating a new response. For example (PXXX):

@@

\emph{Continuation riffing} is the strategy of creating another idea that cannot be understood without the context of the previous. For example (PXXX):

@@

%The strategies above describe techniques for taking one idea and transforming it into another.
In this section, we describe patterns of \emph{where} participants implemented strategies.

@@

Finally, some participants \emph{pair} their riffs. Paired riffing is a special case on linear riffing in which only a single riffed idea is produced. For example, paired repeat riffing from PXXX:

@@

\begin{itemize}
    \item use old parts to make a new device
    \item old parts can use to make something
    %\item create a new device
\end{itemize}

In these responses, there is a recommendation that we produce new electronics, but it is unclear what we would make.

There are four sub-strategies of partial solutions: problem scoping without solution, goal without plan, plan without goal, and passing the problem.

In some responses, an end goal has been established, but executing the goal requires additional information. We call this strategy \emph{goal without plan}. The above responses are examples of the goal without plan strategy.

@@

@@

Above, we described the problem scoping strategy. Some participants performed \emph{problem scoping without solution}, in which problem scoping is the only component of the response.
For example (PXXX): "Remove glass screen to make something". In this case, the participant has provided a scoping of the problem (focus on the glass component) but has not actually provided a solution to the scoped problem.

@@

In this case, a third party must determine what to do with broken MP3 players.

@@

In this section, we DESCRIBE how strategies were employed by participants. The primary author again coded 30 randomly selected runs (5 from each condition, 1150 instances total) for the strategies identified above. Note that examples of riffing identified in this section are distinct from the category tree identification of riffing described in the method section above. The prevalence of each strategy is given in Figure FIG.

%\begin{table}
%    \begin{tabular}{r | l l}
%        \textbf{strategy} & \textbf{\# instances} & \textbf{\% of instances} \\
%        inward scoping & 267 & 23.2 \\
%        outward scoping & 828 & 72 \\
%        no scoping & 55 & 4.8 \\
%        \hline \hline
%        hold riffing & 278 & 24.2 \\
%        continuation riffing & 3 & 0.3 \\
%        repeat riffing & 119 & 10.3 \\
%        generalization riffing & 48 & 4.2 \\
%        \hline
%        any riffing & 448 & 39.0 \\
%        pair & 108 & 9.4 \\
%        reach back & 129 & 11.2 \\
%        \hline \hline
%        scoping without solution & 3 & 0.3 \\
%        passing the problem & 69 & 6 \\
%        plan without goal & 58 & 5.0 \\
%        goal without plan & 58 & 5.0 \\ 
%        \hline
%        any partial solution & 188 & 16.3 \\
%    \end{tabular}
%\end{table}

@@

Outward scoping is by far the most common strategy, occurring in 72\% of instances. Riffing is also very common, with 40\% of instances employing some form of riffing. Riffs are most often consecutive (linear riffing), and hold riffing is the most common type.

@@

The distributions of strategy occurence across position in run tend towards uniform. The notable exceptions are problem scoping and reach-backs. There are fewer occurences of the inward scoping strategy later in brainstorming runs.
The number of reach-backs increase with position.

@@

\begin{itemize}
\item With displays - could be attached to a small solar panel (like the USB chargers w/multi attachments, including solar and car, etc.) and all the power could be sent to the screen as a small, portable light, then sent to countries lacking power in rural areas.
\item They could be loaded with coordinates or other info and sealed in containers, then used in ocean current studies - once the container was collected they could be plugged in and read, and the data could be sent to whomever.
%\item They could be plugged in at a base camp at the bottom of Everest, and then potential climbers could record their name, loved ones' address, and any last words before attempting the climb. 
\end{itemize}

This individual's responses raised the observed uniqueness of ideas in the 75 condition. 
In contrast, other individuals filled their quotas with excessive repeat riffing chains.

### 2013-10-18 chi2014/related.tex
down to 11 pages...

\subsection{Crowdsourced Brainstorming}
The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated environments are possible, such as those that forward ideas that others have generated (electronic brainstorming). 
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
We constrain our focus to nominal brainstorming in this environment with the goal of establishing baselines.

@@

Little et el. compared the iterative and parallel human computation processes on a brainstorming task for names for fabricated companies \cite{little2010exploring}. In the iterative condition, participants saw all names suggested by previous participants. Participants in the parallel condition worked in isolation without seeing other participants' ideas. The parallel process was found to be more likely to generate names with high ratings, advocating the case for nominal brainstorming. The study did not mention categorization of generated ideas, an important measure on flexibility of idea generation \cite{lewis2011affective, nijstad_how_2006, finke1992creative, shah2003metrics}. Each participant also generated only five ideas, leaving the number of ideas requested per participant an open dimension to be explored.

The nature of the microtask marketplace may also require alternative ways of structuring the brainstorming activity.
% calls for an alternative structure for brainstorming tasks in this setting. Researchers have found that 30\% or more submission on Mechanical Turk may be low quality \cite{kittur2008crowdsourcing}. For example, submissions to a brainstorming task for a company name are sometimes grammartically awkward or offensive \cite{little2010exploring}. These low quality responses were not found in walk-in brainstorming studies. 
For example, Bernstein et al. found high variance of effort from Amazon Mechanical Turk workers \cite{soylent}. They characterized two worker personas at opposite ends of the effort spectrum: the {\em Eager Beaver\/} who goes beyond task requirement and the {\em Lazy Turker\/} who does as little work as necessary. Given this finding, a brainstorming task that asks participants to generate as many ideas as they can in a fixed time period might not be cost-effective, since a {\em Lazy Turker\/} can simply fill in a few ideas and wait for the time to run out instead of exerting full effort.

>>>>

\subsection{Crowdsourced Brainstorming}
%The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated environments are possible, such as those that forward ideas that others have generated (electronic brainstorming). 
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
We constrain our focus to nominal brainstorming in this environment with the goal of establishing baselines.

@@

Little et el. compared the iterative and parallel human computation processes on a brainstorming task for names for fabricated companies \cite{little2010exploring}. In the iterative condition, participants saw all names suggested by previous participants. Participants in the parallel condition worked in isolation without seeing other participants' ideas. The parallel process was found to be more likely to generate names with high ratings, advocating the case for nominal brainstorming. The study did not mention categorization of generated ideas, an important measure on flexibility of idea generation \cite{lewis2011affective, nijstad_how_2006, finke1992creative, shah2003metrics}, nor did it explore requesting more than five ideas.

The nature of the microtask marketplace may also require alternative ways of structuring the brainstorming activity.
% calls for an alternative structure for brainstorming tasks in this setting. Researchers have found that 30\% or more submission on Mechanical Turk may be low quality \cite{kittur2008crowdsourcing}. For example, submissions to a brainstorming task for a company name are sometimes grammartically awkward or offensive \cite{little2010exploring}. These low quality responses were not found in walk-in brainstorming studies. 
For example, Bernstein et al. found high variance of effort from Amazon Mechanical Turk workers \cite{soylent}. They characterized two worker personas at opposite ends of the effort spectrum: the {\em Eager Beaver\/} who goes beyond task requirement and the {\em Lazy Turker\/} who does as little work as necessary.

### 2013-10-18 chi2014/results.tex
down to 11 pages...

\subsubsection{Originality}

The increase in o-score over time in Figures~\ref{fig:idea_oscore_order} and \ref{fig:cat_oscore_order} also supports hypothesis 3, the notion that ideas generated in the second half a brainstorming session have higher o-scores than those in the first half. We test a stronger guarantee of this hypothesis that is implied by our data: that ideas after the first 20 have higher o-scores than the first 20.

Partitioning the data into instances $\leq20$ and $\textgreater20$, we found that these distributions of o-scores are best modeled using beta distributions. Figures~\ref{fig:idea_oscore_hyp4} and \ref{fig:cat_oscore_hyp4} show the data and fitted models. We found significant differences between model parameters, confirming hypothesis 3.

Collectively, these results provide a guideline for maximizing originality in brainstorming tasks on microtask marketplaces: it is more effective to solicit $\textgreater20$ ideas from a smaller pool of participants than to ask for fewer ideas from more individuals.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{hyp4_ideas}
    \caption{Beta models for idea o-score}
    \label{fig:idea_oscore_hyp4}
    \includegraphics[width=0.9\columnwidth]{hyp4_cats}
    \caption{Beta models for category o-score}
    \label{fig:cat_oscore_hyp4}
\end{figure}

@@

In our clustered data, we can identify riffing by examining whether a response instance belongs to the same category tree as the previous instance. We can then derive a number of statistics from these data.

To contextualize this process, below is an excerpt of a particular participant's brainstorming run.

@@

The participant first touches on the general idea of recycling, then becomes more specific by reducing the scope of recycling to specific parts. Finally, they limit the scope of parts to precious metals, particularly gold. At this point, the participant exhausts their working memory of the category and moves on.

@@

SIAM predict that individuals will generate ideas from an idea category until they exhaust that category, at which point they switch to another category (hypothesis 4). Furthermore, SIAM predicts that this category switching will be observable as taking more time to generate an idea in a new category than in the existing category (hypothesis 5). We examine each of these hypotheses in turn.

@@

The resulting models fitted to the data are shown in Figure~\ref{fig:hyp5_comparison}. The mean for the within-category condition was 9.5 in log space (13.4 seconds, HDI 9.4-9.6), while the mean for the between-categories condition was 10.2 (27.0 seconds, HDI 10.2-10.3). The differences in mean are significant and confirm hypothesis 5. Notably, within-category instance generation took an average of 12.6 seconds less than between-categories instance generation, consistent with the findings of Nijstad and Stroebe, who reported differences of 6-12 seconds between these two idea generation processes.

>>>>

The above plots also suggest that there is a pivot point around 20 ideas after which o-scores are higher.

%The increase in o-score over time in Figures~\ref{fig:idea_oscore_order} and \ref{fig:cat_oscore_order} also supports hypothesis, the notion that ideas generated in the second half a brainstorming session have higher o-scores than those in the first half. We test a stronger guarantee of this hypothesis that is implied by our data: that ideas after the first 20 have higher o-scores than the first 20.

Partitioning the data into instances $\leq20$ and $\textgreater20$, we found that these distributions of o-scores are best modeled using beta distributions. Figure~\ref{fig:idea_oscore_hyp4} shows the data and fitted models. We found significant differences between model parameters.
Collectively, these results provide a guideline for maximizing originality in brainstorming tasks on microtask marketplaces: it is more effective to solicit $\textgreater20$ ideas from a smaller pool of participants than to ask for fewer ideas from more individuals.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{hyp4_ideas}
    \caption{Beta models for idea o-score}
    \label{fig:idea_oscore_hyp4}
    %\includegraphics[width=0.9\columnwidth]{hyp4_cats}
    %\caption{Beta models for category o-score}
    %\label{fig:cat_oscore_hyp4}
\end{figure}

@@

We can identify riffing by examining whether a response instance belongs to the same category tree as the previous instance. We can then derive a number of statistics from these data. Below is an excerpt of a particular participant's brainstorming run.

@@

The participant first touches on the general idea of recycling, then becomes more specific by reducing the scope of recycling to specific parts, and then to precious metals.

@@

SIAM predict that individuals will generate ideas from an idea category until they exhaust that category, at which point they switch to another category (hypothesis 3). Furthermore, SIAM predicts that this category switching will be observable as taking more time to generate an idea in a new category than in the existing category (hypothesis 4). We examine each of these hypotheses in turn.

@@

The resulting models fitted to the data are shown in Figure~\ref{fig:hyp5_comparison}. The mean for the within-category condition was 9.5 in log space (13.4 seconds, HDI 9.4-9.6), while the mean for the between-categories condition was 10.2 (27.0 seconds, HDI 10.2-10.3). The differences in mean are significant and confirm hypothesis 4. Notably, within-category instance generation took an average of 12.6 seconds less than between-categories instance generation, consistent with the findings of Nijstad and Stroebe, who reported differences of 6-12 seconds.
